Discovery of Mg-depleted and K-enhanced Stars in \textit{LAMOST}

### 2018-01-31 article/ms.tex
adjusted authors to preliminary ordering
included modified K vs gmog figures, modfified table, and todo'd sections that could conceivably be deleted to meet page limit

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Mathew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
Amanda I. Karakas,$^{1}$
John C. Lattanzio,$^{1}$
Kevin C. Schlaufman,$^{3}$\newauthor
Anna Y.Q Ho,$^{4}$
Melissa K. Ness,$^{5}$
David W. Hogg, $^{6}$
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{4}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
}

@@

Stellar absorption spectra act as a fossil record of the conditions where the stars form. Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with  depleted Mg and enhanced K abundances have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 113 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios. These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419. These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.

@@

An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.

A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}. The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters. It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway. The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.

@@

Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena. In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates. In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed. Section \ref{sec:conclusion} summarises the main results.

@@

These filters identified 384 unique stars to be vetted manually. We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$ wavelengths. The distilled catalogue contains \todo{113} candidate stars enhanced in K and depleted in Mg.

@@

The presence of Na enhancements were visually estimated from the sample of 113 candidate stars' flux spectra. Flux based estimates placed at most 40 of the 113 stars (35\%) as being likely Na enhanced targets. Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{KvsMgab.png}
    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The dotted line is arbitrary, and is present simply as a visual aide.}
    \label{KvsMg}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters. None of the stars appear to be associated with NGC 2419 or NGC 2808. From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}. This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.

@@

\subsection{Abundances}
\label{sec:abundances}
Figure \ref{KvsMg} shows [K/Fe]  for the 113 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra, these being similar to the [$\alpha$/Fe] abundances from \tc.

@@

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, which is absent from measurements in the Milky Way. This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases. It is interesting that the Mg-poor population of NGC 2419 appears to fit this relation.

However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of processing rather than a physical relation. Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.

The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although its possible a slight depletion is present. No variation with metallicity is observed for [$\alpha$/Fe].

@@

[Na/Fe] was also measured for the \lamost\ data. Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}. However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels. It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.

@@

The 113 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and a range of metalicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

@@

\label{sec:scenarios}
\begin{table*}
\centering
\begin{tabular}{llllllllll}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Vr (km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{[Fe/H]} & \textbf{[Alpha/Fe]} & {$\boldsymbol \chi^\textbf{2}$} \\ \hline
J060142.80+132321.4 & 90.43 & 13.39 & 45 & 33.28 & 4858 & 2.57 & -0.30 & 0.10 & 0.24 \\ \hline
J075043.12+204658.0 & 117.68 & 20.78 & 47 & 52.46 & 4795 & 2.53 & -0.47 & 0.06 & 0.40 \\ \hline
J032450.35+352401.8 & 51.21 & 35.40 & 143 & 95.63 & 4908 & 3.33 & -0.27 & 0.19 & 0.70 \\ \hline
J214721.25+023958.7 & 326.84 & 2.67 & 104 & -63.83 & 4649 & 2.22 & -0.68 & 0.26 & 0.81 \\ \hline
J040340.38+563902.4 & 60.92 & 56.65 & 30 & 39.87 & 4459 & 2.05 & -0.46 & 0.01 & 0.61 \\ \hline
J035455.85+594730.3 & 58.73 & 59.79 & 57 & -40.17 & 4956 & 2.81 & 0.08 & 0.04 & 0.56 \\ \hline
J035928.29+595932.8 & 59.87 & 59.99 & 35 & -38.07 & 4808 & 2.44 & -0.53 & 0.16 & 0.32 \\ \hline
J034458.82+592955.1 & 56.25 & 59.50 & 53 & -32.68 & 4811 & 2.66 & 0.06 & 0.10 & 0.64 \\ \hline
J220657.78+232138.3 & 331.74 & 23.36 & 50 & -27.58 & 4842 & 3.34 & -0.40 & 0.10 & 0.23 \\ \hline
J061323.14+325543.0 & 93.35 & 32.93 & 39 & -25.78 & 4861 & 2.51 & -0.40 & 0.16 & 0.42 \\ \hline
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 \\ \hline
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 \\ \hline
J040817.31+463252.5 & 62.07 & 46.55 & 92 & -1.80 & 5019 & 2.68 & -0.09 & 0.05 & 0.98 \\ \hline
J072156.18+225405.3 & 110.48 & 22.90 & 101 & -46.77 & 4840 & 2.54 & -0.33 & 0.17 & 0.69 \\ \hline
J040634.97+411354.9 & 61.65 & 41.23 & 45 & -35.38 & 4770 & 2.67 & -0.26 & 0.07 & 0.51 \\ \hline
J041608.62+433504.7 & 64.04 & 43.58 & 30 & -20.09 & 4967 & 2.90 & -0.17 & 0.04 & 0.33 \\ \hline
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 \\ \hline
J052924.25+494319.7 & 82.35 & 49.72 & 94 & -22.48 & 5087 & 3.12 & -0.35 & 0.11 & 0.70 \\ \hline
J061427.58+331544.3 & 93.61 & 33.26 & 51 & 3.30 & 4468 & 1.87 & -0.41 & 0.11 & 0.67 \\ \hline
J062128.63+343545.8 & 95.37 & 34.60 & 39 & 33.28 & 4831 & 2.58 & -0.23 & 0.08 & 0.27 \\ \hline
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 \\ \hline
J120032.60+024438.2 & 180.14 & 2.74 & 97 & 166.98 & 4633 & 2.33 & -0.93 & 0.26 & 0.89 \\ \hline
J163910.01+100545.3 & 249.79 & 10.10 & 39 & 123.81 & 4663 & 2.46 & -0.58 & 0.03 & 0.61 \\ \hline
\end{tabular}
\caption{Placeholder table}
\label{my-label}
\end{table*}

@@

This spread in metallicity is important: taken in isolation, it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the evolutionary history of our galaxy. Rather, these stars appear to be continuously forming in successive generations.

@@

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through binary accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope. In this scenario, it is observations of this smaller binary companion star that make up our sample of 113 giants.

Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation. The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.

@@

The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419. If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 113 field star sample.

@@

This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars. But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form. Thus it provides a way of linking the current observations of our 113 candidate stars with the observations of NGC 2419. Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.

However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).

@@

\section{Conclusions}
\label{sec:conclusion}
Of the 454180 giant sample from \lamost, 113 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra. These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects. The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.

@@

\begin{comment}
\begin{table}[H]
\centering
\begin{tabular}{llllllllll}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{Radial\_Velocity\_(km/s)} & \textbf{Teff} & \textbf{Logg} & \textbf{{[}Fe/H{]}} & \textbf{{[}Alpha/Fe{]}} & \textbf{$\chi^2$} \\ \hline
J234942.32+300654.0 & 357.43 & 30.11 & 20 & -195.46 & 4004 & 1.12 & -0.58 & 0.23 & 2.73 \\ \hline
J065334.23+131639.7 & 103.39 & 13.28 & 7 & 179.88 & 4896 & 2.61 & -0.71 & 0.02 & 0.18 \\ \hline
J112309.75+261255.9 & 170.79 & 26.22 & 3 & 113.02 & 4273 & 1.13 & -1.35 & 0.17 & 0.09 \\ \hline
J111651.71+253038.5 & 169.22 & 25.51 & 6 & 102.83 & 4658 & 2.90 & -0.50 & 0.02 & 0.08 \\ \hline
J045424.86+534628.5 & 73.60 & 53.77 & 6 & -36.57 & 4451 & 1.81 & -0.19 & 0.07 & 0.37 \\ \hline
J065857.80+081714.8 & 104.74 & 8.29 & 12 & 26.68 & 5070 & 3.30 & -0.61 & 0.10 & 0.18 \\ \hline
J045544.93+490023.3 & 73.94 & 49.01 & 6 & -38.07 & 4717 & 2.55 & -0.34 & 0.11 & 0.11 \\ \hline
J040739.62+423724.4 & 61.92 & 42.62 & 9 & -37.77 & 4075 & 1.54 & -0.32 & 0.08 & 0.28 \\ \hline
J043121.48+414757.2 & 67.84 & 41.80 & 8 & -12.59 & 4537 & 2.07 & -0.09 & 0.03 & 0.13 \\ \hline
J041900.21+422223.9 & 64.75 & 42.37 & 12 & -34.18 & 4263 & 1.77 & -0.55 & 0.09 & 0.28 \\ \hline
J041209.44+411801.0 & 63.04 & 41.30 & 35 & -20.69 & 4767 & 2.24 & -0.26 & 0.12 & 0.91 \\ \hline
J063648.82+130723.3 & 99.20 & 13.12 & 8 & 85.74 & 4925 & 2.93 & -0.57 & -0.03 & 0.19 \\ \hline
J070524.04+120351.0 & 106.35 & 12.06 & 19 & 60.26 & 4754 & 2.64 & -0.56 & -0.02 & 0.24 \\ \hline
J063501.25+134744.6 & 98.76 & 13.80 & 7 & 47.67 & 4612 & 2.33 & -0.40 & 0.01 & 0.19 \\ \hline
J053942.83+383727.8 & 84.93 & 38.62 & 18 & -85.74 & 4979 & 2.26 & -0.66 & 0.23 & 0.27 \\ \hline
J053123.26+421952.0 & 82.85 & 42.33 & 8 & 41.07 & 4785 & 2.59 & -0.26 & 0.01 & 0.26 \\ \hline
J052643.65+354130.3 & 81.68 & 35.69 & 9 & -18.89 & 4914 & 2.73 & -0.09 & 0.03 & 0.28 \\ \hline
J064618.82+050545.8 & 101.58 & 5.10 & 9 & 85.74 & 4772 & 2.66 & -0.49 & -0.01 & 0.28 \\ \hline
J063719.82+185602.6 & 99.33 & 18.93 & 5 & 15.29 & 5075 & 2.94 & -0.12 & 0.03 & 0.10 \\ \hline
J072912.52+073436.9 & 112.30 & 7.58 & 9 & 117.52 & 4835 & 3.18 & -0.44 & 0.33 & 0.34 \\ \hline
J193217.91+374505.6 & 293.07 & 37.75 & 28 & -70.15 & 4982 & 2.62 & -0.48 & 0.33 & 0.55 \\ \hline
J192937.24+390211.0 & 292.41 & 39.04 & 6 & -52.16 & 4819 & 3.00 & 0.37 & 0.12 & 0.21 \\ \hline
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 \\ \hline
J235454.61+110356.9 & 358.73 & 11.07 & 12 & -109.72 & 4794 & 3.07 & -0.16 & 0.30 & 0.21 \\ \hline

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Kemp et al.]{
Alex J. Kemp,$^{1}$\thanks{E-mail: ajkem1@student.monash.edu}
Andrew R. Casey,$^{1,2}$
Mathew T. Miles,$^{1}$
Brodie J. Norfolk,$^{1}$\newauthor
John C. Lattanzio,$^{1}$
Amanda I. Karakas,$^{1}$
Kevin C. Schlaufman,$^{3}$\newauthor
Anna Y.Q Ho,$^{4}$
Melissa K. Ness,$^{5}$
David W. Hogg, $^{6}$
\\
% List of institutions
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$ Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$, Department of Physics and Astronomy, Johns Hopkins University, Baltimore, MD 21218, USA\\
$^{4}$ Cahill Center for Astrophysics, California Institute of Technology, MC 249-17, 1200 E California Blvd, Pasadena, Ca, 91125, USA\\
$^{5}$ Max-Planck-Institut f$\ddot{u}$r Astronomie, K$\ddot{o}$nigsthul 17, D-69117 Heidelberg, Germany\\
$^{6}$ Center for Cosmology and Particle Physics, Department of Physics, New York University, 4 Washington Pl., room 424, New York, NY, 10003, USA\\
}

@@

Stellar absorption spectra act as a fossil record of the conditions where the stars form. Stars with unusual elemental abundances are of particular interest; these rare stars often offer clues about rare astrophysical events or nucleosynthetic pathways. Stars with  depleted Mg and enhanced K abundances have thus far only been found in the two massive globular clusters NGC 2419 and NGC 2808. The origin of this abundance signature remains unknown, as does the reason for its apparent exclusivity to these two globular clusters. Here we present 112 candidate field stars identified from \LamostGiants \ giants observed by \lamost \ that have slightly depleted [Mg/Fe] and significantly enhanced [K/Fe] abundance ratios. These stars re present at a range of metallicities, and none have abundances that are as extreme as those in NGC 2419. These candidate stars should provide guidance for follow up surveys and modelling attempts attempting to determine the origin of the Mg-K anti-correlation.

@@

\todo{An early modelling attempt at replicating the anomalous Mg/K abundances assumed hot-bottom burning in AGB and super-AGB (SAGB) stars \citep{ventura2012}. This study succeeded in reproducing the Mg-K anti-correlation through the nuclear reaction pathway \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(e^-,\nu)^{37}Cl(p,\gamma)^{38}Ar(p,\gamma)^39K} (corrected as per \cite{iliadis2016}) for the production of K. However, abundance patterns consistent with NGC 2419 were only possible if the reaction cross section was set to 100 times the commonly accepted value or if the temperature at the base of the envelope could be made to exceed $\sim$ 150 MK.}

A more recent attempt to replicate the Mg/K abundance signature in NGC 2419 by \cite{iliadis2016} also targetted abundances of Si, Sc, Ca, Ti and V, elements reported as having weak correlations with Mg by \cite{cohenkirby2012}. The ultimate goal was to constrain the temperatures and densities required to produce the chemical signature, and thereby provide insight into potential polluters. \todo{ It is perhaps noteworthy that they identified a different main reaction pathway for K nucleosynthesis to that of \cite{ventura2012}, which is relegated to a minor secondary pathway. The main pathway they identify is \ce{^{36}Ar(p,\gamma)^{37}K(\beta ^+ \nu)^{37}Ar(p,\gamma)^{38}K(\beta ^+ \nu)^{38}Ar(p,\gamma)^39K}.}

@@

Here we use \lamost\ data to conduct the largest ever search for field stars that are enhanced in potassium and depleted in magnesium. The discovery (or non-discovery) of such stars will guide models that attempt to explain the Mg-K anti-correlation and related abundance phenomena.\todo{ In Section \ref{sec:method} we outline our methods to identify candidates enhanced in K and depleted in Mg, and the follow-up observations and abundance analysis of those candidates. In Section \ref{sec:discussion} the results and their implications on possible poluters are discussed. Section \ref{sec:conclusion} summarises the main results.}

@@

These filters identified 384 unique stars to be vetted manually. We visually inspected every candidate (multiple times) and excluded any candidate that showed any evidence of being a false positive, including candidates that exhibited data reduction issues, apparent absorption that was narrower than the expected spectral resolution, as well as 75 stars that exhibited chromospheric emission at H$\alpha$ wavelengths. The distilled catalogue contains \todo{112} candidate stars enhanced in K and depleted in Mg.

@@

\todo{The presence of Na enhancements were visually estimated from the sample of 112 candidate stars' flux spectra. Flux based estimates placed at most 40 of the 112 stars (35\%) as being likely Na enhanced targets.} Na abundances calculated from the \lamost\ spectra later revealed 30\% of the target stars with Na above 0.5 dex. \todo{@andy add anything specific to Na abundance methods from LAMOST}.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{Kvsmgmod.png}
    \caption{Comparison of [K/Fe] vs [$\alpha$/Fe] for the candidate stars with [K/Fe] vs [Mg/Fe] abundances for NGC 2419 and NGC 2808 \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. The dotted line is arbitrary, and is present simply as a visual aide.}
    \label{KvsMg}
\end{figure}

@@

\subsection{Association with known globular clusters}
\label{sec:globclustasoc}
Our sample was cross-matched against \cite{harris1996}'s data base of globular clusters. None of the stars appear to be associated with NGC 2419 or NGC 2808. \todo{ From the sample, J074807.22+261514.2 is the closest star in the sky to a globular cluster, at 2.54\degree\ separation from Ko 2 \citep{koposov2007}. This separation is large for association with such a small, distant cluster and the star's metallicity and apparent magnitude make it even less likely to be a member.}

@@

\subsection{Abundances}
\label{sec:abundances}
Figure \ref{KvsMg} shows [K/Fe]  for the 112 star sample plotted against $[\alpha$/Fe] and overlaid with [K/Fe] from NGC 2419 and NGC 2808 plotted against [Mg/Fe] \citep{cohenkirby2012, mucciarelli2012, mucciarelli2015}. [K/Fe] vs [Mg/Fe] for the three stars from the sample observed using Magellan/MIKE is also shown. The use of [$\alpha$/Fe] as a proxy for [Mg/Fe] is supported by the [Mg/Fe] measurements from the high-resolution spectra, these being similar to the [$\alpha$/Fe] abundances from \tc.

@@

The candidate stars' [K/Fe] also exhibits an interesting anti-correlation with total metallicity, shown in Figure \ref{KvsFe}, \todo{which is absent from measurements in the Milky Way}. This may be consistent with a (somewhat) constant level of [K/H] between each star, which would then cause [K/Fe] to fall as [Fe/H] increases. It is interesting that the Mg-poor population of NGC 2419 appears to fit this relation.

However, for reasons related to the use of both a data-driven model and a physical model for calculating abundances \todo{@andy add any elaboration on what the problem was, if necessary}, it is possible that this effect is an artefact of abundance processing rather than a physical relation. Without further observations of the sample stars, we are unable to say with certainty whether this phenomena is real or not.

The candidate stars' levels of [$\alpha$/Fe] were generally consistent with galactic levels of [Mg/Fe], although again it's possible a slight depletion is present. No variation with metallicity is observed for [$\alpha$/Fe].

@@

[Na/Fe] was also measured for the \lamost\ data. Two distinct populations were observed, with a substantial minority of approximately 30\% of the sample having [Na/Fe] > 0.5, significantly higher than typical galactic abundances of [Na/Fe] $\lesssim$ 0.3 \citep{kobayashi2011}. However, this behaviour is very likely due to the effect of interstellar dust; it was found that the values of E(B-V), taken from IRSA's all-sky dust map \citep{schlafly2011}, were higher for the stars supposedly enriched in Na than for those displaying galactic levels. \todo{It worth mentioning briefly that the modelling work of \cite{prantzos2017} predicted an anti-correlation between Na and K in a 180 MK hydrogen burning environment appropriate to NGC 2808, while observational data for NGC 2808 implies a correlation between Na and K. For these newly identified candidate stars, neither relation between [K/Fe] and [Na/Fe] beyond probable dust effects is observed.}

@@

The 112 star candidate pool of K enhanced and potentially Mg depleted stars represent a unique collection of stars; while not as K enhanced as the extreme population in NGC 2419, they exhibit K abundances well above typical galactic levels and exist at a range of metalicities. It seems likely that whatever process is responsible for these anomalous field stars is similar to whatever caused the unusual stellar populations in NGC 2419 and NGC 2808.

@@

\label{sec:scenarios}
\begin{table*}
\centering
\caption{Tabulated data for 10 of the 112 candidate stars. Data for the full sample is available online.}
\label{my-label}
\begin{tabular}{cccccccccccccc}
\hline
\textbf{2MASSID} & \textbf{RA} & \textbf{DEC} & \textbf{S/N} & \textbf{V$_\textrm{r}$} & \textbf{T$_\textrm{eff}$} & $\boldsymbol \log{ \, \textbf{g}}$ & \textbf{{[}Fe/H{]}} & \textbf{{[}$\alpha$/Fe{]}} & \textbf{$\boldsymbol \chi_r ^\textbf{2}$} & \textbf{{[}K/Fe{]}} & \textbf{Error} & \textbf{{[}Na/Fe{]}} & \textbf{Error} \\ 
- & {[}deg{]} & {[}deg{]} & [pixel$^{-1}]$ & {[${\rm km\,s}^{-1}$]} & {[}K{]} & $[{\rm cm\,s}^{-2}]$ & {[}dex{]} & {[}dex{]} & - & {[}dex{]} & {[}dex{]} & {[}dex{]} & {[}dex{]} \\ \hline
J000908.89+124821.9 & 2.29 & 12.81 & 10 & -78.55 & 4892 & 2.82 & -0.12 & 0.33 & 0.19 & 1.08 & 0.16 & 0.86 & 0.12 \\
J002619.36+565612.1 & 6.58 & 56.94 & 31 & -39.57 & 4205 & 1.49 & 0.22 & 0.06 & 0.76 & 0.62 & 0.08 & 0.39 & 0.10 \\
J002907.61+354701.0 & 7.28 & 35.78 & 15 & -82.74 & 5116 & 3.56 & 0.24 & 0.17 & 0.18 & 1.01 & 0.06 & -0.20 & 0.00 \\
J003451.10+424543.0 & 8.71 & 42.76 & 15 & -79.15 & 4460 & 2.10 & -0.56 & 0.24 & 0.31 & 0.96 & 0.26 & -0.16 & 0.00 \\
J005649.98+391722.9 & 14.21 & 39.29 & 41 & -46.77 & 4578 & 2.67 & 0.31 & 0.10 & 0.44 & 0.76 & 0.11 & -0.02 & 0.00 \\
J010305.95+043445.9 & 15.77 & 4.58 & 90 & 20.69 & 4646 & 2.72 & 0.10 & 0.05 & 1.17 & 0.95 & 0.06 & -0.07 & 0.00 \\
J011949.36+063411.4 & 19.96 & 6.57 & 479 & -28.18 & 4820 & 2.61 & -0.29 & 0.09 & 2.38 & 1.03 & 0.00 & -0.04 & 0.00 \\
J013039.08+404843.8 & 22.66 & 40.81 & 71 & -80.34 & 4355 & 2.01 & -0.09 & 0.14 & 0.93 & 0.92 & 0.05 & 0.46 & 0.05 \\
J030101.42+560042.3 & 45.26 & 56.01 & 88 & -39.27 & 4878 & 2.53 & -0.32 & 0.09 & 0.67 & 1.00 & 8.70 & -0.02 & 0.00 \\
J032423.46+425429.6 & 51.10 & 42.91 & 23 & -56.74 & 4649 & 2.63 & -0.11 & -0.01 & 0.34 & 1.12 & 0.09 & 0.80 & 0.04 \\ \hline
\end{tabular}
\end{table*}

@@

This spread in metallicity is important: taken in isolation, it implies that the process responsible for this signature, rare as it is, is not necessarily tied to a certain epoch in the evolutionary history of our galaxy. Rather, these stars appear to be continuously forming \todo{ in successive generations}.

@@

The SAGB star produces K (destroying Na in the process \citep{prantzos2017}) which is then mixed throughout its envelope. It then deposits its K rich outer layers onto its smaller companion through binary accretion. This smaller companion would continue to evolve long after the SAGB star has formed a white-dwarf remnant and will, depending on its mass after accretion, either undergo hot-bottom burning or, more likely, will not. If the companion star had sufficient mass to undergo hot bottom burning, then Na could be produced and Mg depleted \citep{prantzos2017}, with this material mixed throughout the envelope. In this scenario, it is observations of this smaller binary companion star that make up our sample of 112 giants.

Although this scenario allows for consistency with the total spread in metallicity, it doe not account for the uniqueness of the signal to NGC 2419 and NGC 2808 among globular clusters, nor does it satisfactorily explain why such a large proportion of stars in NGC 2419 exhibit the Mg-K anti-correlation. \todo{The idea that 30\% of the stars in NGC 2419 were once in a binary with SAGB stars is highly unlikely, to say the least.}

@@

The anti-correlation between [K/Fe] and [Fe/H] could be interpreted as a relatively constant level of [K/H] present in at least one region of star forming gas, resulting in a steady decrease in [K/Fe] as [Fe/H] increases. This interpretation is somewhat supported by the consistency of the relation with levels of [K/Fe] in NGC 2419. If this relation is real, we can perhaps -- without saying anything about the polluter star -- use it to motivate an evolutionary sequence that can account for observations of [K/Fe] and [Mg/Fe] both in NGC 2419 and our new 112 field star sample.

@@

This cycle allows for the Mg depletions to be preserved in globular clusters, where even the most massive clusters only form at most 2 generations of stars. But it also allows the Mg signal to effectively be lost within the disc of the galaxy, where many generations of stars may form. Thus it provides a way of linking the current observations of our 112 candidate stars with the observations of NGC 2419. Certainly the idea that both groups of anomalous stars arise from the same polluter source must be entertained.

\todo{However, beyond the question of whether the [K/Fe]-[Fe/H] anti-correlation is real or not, the extreme difficulty of forming a cloud of Mg depleted, K enriched material in the first place must be emphasized. Indeed, if we assume the primordial abundances (pre-mystery event) are similar to those of NGC 2419's Mg-normal population, then it is impossible. If the primordial cloud already has [Mg/Fe]$\approx 0.5$, to reduce this necessitates the addition of large amounts of iron rich material that is also very depleted in [Mg/Fe]. But as soon significant amounts of iron are added, [Fe/H] for the subsequent the Mg-depleted population should increase, while no significant [Fe/H] variation between the two populations is observed \citep{cohenkirby2012, mucciarelli2012}. This implies that the mystery polluter star may have released its material into an environment enriched only by Big-Bang Nucleosynthesis (BBNS).}

@@

\section{Conclusions}
\label{sec:conclusion}
Of the 454180 giant sample from \lamost, 112 candidate stars were identified as likely to have enhanced K and depleted Mg based on their absorption spectra. These stars show every appearance of being field stars, nor do they have the hallmarks of being the product of NLTE effects. The candidate sample reflected the metallicity distribution of the base \textit{LAMOST} sample.

@@
